---
title: "R Notebook"
output: html_notebook
---

Importing Data, Removing null values
```{r}
df <- read.csv("Books_Data_Clean.csv")
df <- df[complete.cases(df), ]
print(df)
```

Checking null values are removed
```{r}
print(colSums(is.na(df)))
```

Splitting categorical and numeric columns
```{r}
numeric_df <- df[, sapply(df, is.numeric)]
categorical_df <- df[, !sapply(df, is.numeric)]

print(numeric_df)
print(categorical_df)
```

Relabeling genre fiction to just fiction
```{r}
old <- c("genre fiction")
new <- c("fiction")
categorical_df$genre <- ifelse(categorical_df$genre %in% old, new[match(categorical_df$genre, old)], categorical_df$genre)

print(categorical_df$genre)
```


Creating a correlation matrix to analyze relationships
```{r}
corr_matrix <- cor(numeric_df)
print(corr_matrix)
```

All Notable Relationships
1. Moderate Positive -- Gross Sales, Rating Count
2. Weak Positive -- Revenue, Ratings Count
3. Strong Negative -- Sales Rank, Ratings Count
4. Strong Positive -- Revenue, Sales
5. Weak Negative -- Rank, Sales
6. Weak Positive -- Price, Revenue
7. Weak Negative -- Rank, Revenue

Converting categorical data we want to use to numeric data
```{r}
genre_mappings <- c("fiction" = 1, "nonfiction" = 2, "children" = 3)
author_rating_mapping <- c("Novice" = 1, "Intermediate" = 2, "Excellent" = 3, "Famous" = 4)

genre_encoded <- genre_mappings[categorical_df$genre]
author_rating_encoded <- author_rating_mapping[categorical_df$Author_Rating]

print(genre_encoded)
print(author_rating_encoded)
```

Adding the converted categorical data back to the numeric data set
```{r}
numeric_df$genre <- genre_encoded
numeric_df$author_rating <- author_rating_encoded

print(numeric_df)
```

Running another correlation matrix with the newly added columns
```{r}
corr_matrix <- cor(numeric_df)
print(corr_matrix)
```
New Notable Relationships
Strong Positive -- Book Rating, Author Rating

Histograms of the data to see how things lie
```{r}
hist(numeric_df$Book_average_rating, main = "Book Average Rating", xlab="Rating", 
     ylab = "Amount", col="royalblue")

hist(numeric_df$author_rating, main = "Author Average Rating", xlab="Rating", 
     ylab = "Amount", col="maroon")

hist(numeric_df$units.sold, main = "Units Sold", xlab="Quanitity", 
     ylab = "Amount", col="forestgreen")

hist(numeric_df$Book_ratings_count, main = "Rating Count", xlab="Count", 
     ylab = "Amount", col="azure")

hist(numeric_df$sale.price, main = "Sales Price", xlab="Book Price", 
     ylab = "Amount", col="gold")
```

Scatter Plots of some of the strong relationships
```{r}
plot(numeric_df$sales.rank, numeric_df$Book_ratings_count, 
     main = "Sales Rank vs Rating Count", xlab = "Sales Rank", 
     ylab = "Rating Count", col= "navy", pch = 16)

plot(numeric_df$publisher.revenue, numeric_df$gross.sales, 
     main = "Publisher Revenue vs Gross Sales", xlab = "Publisher Revenue", 
     ylab = "Gross Sales", col= "goldenrod", pch = 16)

plot(numeric_df$gross.sales, numeric_df$Book_ratings_count, 
     main = "Gross Sales vs Book Rating Count", xlab = "Gross Sales", 
     ylab = "Rating Count", col= "darkviolet", pch = 16)

plot(numeric_df$Book_average_rating, numeric_df$author_rating, 
     main = "Average Book Rating vs Author Rating", xlab = "Average Book Rating", 
     ylab = "Author Rating", col= "thistle", pch = 16)
```

Analyzing the self published books
```{r}
self_published <- subset(numeric_df, numeric_df$publisher.revenue == 0)
self_published <- self_published[, -which(names(self_published) == "publisher.revenue")]
print(cor(self_published))
```
Strong Positive -- Book Rating, Author Rating
Moderate Positive -- Rating Count, Gross Sales
Moderate Negative -- Gross Sales, Sales Rank
Strong Negative -- Sales Count, Sales Rank
Small Positive -- Author Rating, Sales Rank

```{r}
print(mean(self_published$gross.sales))
print(mean(numeric_df$gross.sales))

print(mean(self_published$sale.price))
print(mean(numeric_df$sale.price))
```

Making a Scatter Plot comparing self published to base Data set
```{r}
plot(numeric_df$gross.sales, numeric_df$sale.price, col = "steelblue", pch = 16, main = "Comparing Self Published to Base Dataset", xlab = "Gross Sales", ylab = "Sales Price")
points(self_published$gross.sales, self_published$sale.price, col = "darkviolet", pch = 16)
legend("topright", legend = c("Base Dataset", "Self Published Dataset"), col = c("steelblue", "darkviolet"), pch = 16)
```


Analyzing books rated better the 4.5
```{r}
best_rated <- subset(numeric_df, numeric_df$Book_average_rating >= 4.5)
print(best_rated)
print(cor(best_rated))
```

There are no children's books in the top rated, but that can be to due sample
There was no significant difference in genre of book to best rated

Every book rated 4.5 or higher has a famous author (4 is corresponding to famous)
```{r}
print(mean(best_rated$author_rating))
```

```{r}
plot(best_rated$gross.sales, best_rated$sale.price, xlab = "Gross Sales", ylab = "Sales Price",
     main = "Best Rated: Gross Sales vs Sale Price", col = "olivedrab", pch = 16)
```



Making a table of the genre to see how the ratio of fiction to nonfiction
```{r}
count_table <- table(numeric_df$genre)
fiction_pct <- count_table["1"] / nrow(numeric_df)
nonfiction_pct <- count_table["2"] / nrow(numeric_df)


best_seller_table <- table(best_rated$genre)
fiction_pct_b <- best_seller_table["1"] / nrow(best_rated)
nonfiction_pct_b <- best_seller_table["2"] / nrow(best_rated)

print(best_seller_table)

print(paste("Base: Fiction pct: ", fiction_pct, "%, Nonfiction pct: ", nonfiction_pct, "%"))
print(paste("Best Sellers: Fiction pct: ", fiction_pct_b, "%, Nonfiction pct: ", nonfiction_pct_b, "%"))

```
Checking gross sales of 4.5 or higher vs all
```{r}
print(paste(mean(best_rated$gross.sales)))
print(paste(mean(numeric_df$gross.sales)))
```


Analyzing the top 10% of Books ranked
```{r}
top_ten <- subset(numeric_df, numeric_df$sales.rank <= 101)
print(cor(top_ten))
```
Notable Relationships
Strongly Negative -- Units sold, sales rank

Showing the relationship between authors and top 10% ranked books vs all books
```{r}
author_10_count <- table(top_ten$author_rating)
print(mean(top_ten$author_rating))
print(author_10_count)

author_count <- table(numeric_df$author_rating)
print(mean(numeric_df$author_rating))
print(author_count)
```

Compare authors to genres
```{r}
plot(numeric_df$author_rating, numeric_df$genre, xlab = "Author Rating", ylab = "Genre (by #)", pch = 16, col = "darkcyan")

author_genre <- table(numeric_df$author_rating, numeric_df$genre)
print(author_genre)

```

Comparing Author Rating to Gross Sales
```{r}
mean_gross_sales_by_author_rating <- aggregate(gross.sales ~ Author_Rating, data = df, FUN = mean, na.rm = TRUE)
print(mean_gross_sales_by_author_rating)
```


```{r}
print(colors())
```

