---
title: "R Notebook"
output: html_notebook
---

Importing Data, Removing null values
```{r}
df <- read.csv("Books_Data_Clean.csv")
df <- df[complete.cases(df), ]
print(df)
```

Checking null values are removed
```{r}
print(colSums(is.na(df)))
```

Splitting categorical and numeric columns
```{r}
numeric_df <- df[, sapply(df, is.numeric)]
categorical_df <- df[, !sapply(df, is.numeric)]

print(numeric_df)
print(categorical_df)
```

Relabeling genre fiction to just fiction
```{r}
old <- c("genre fiction")
new <- c("fiction")
categorical_df$genre <- ifelse(categorical_df$genre %in% old, new[match(categorical_df$genre, old)], categorical_df$genre)

print(categorical_df$genre)
```


Creating a correlation matrix to analyze relationships
```{r}
corr_matrix <- cor(numeric_df)
print(corr_matrix)
```

All Notable Relationships
1. Moderate Positive -- Gross Sales, Rating Count
2. Weak Positive -- Revenue, Ratings Count
3. Strong Negative -- Sales Rank, Ratings Count
4. Strong Positive -- Revenue, Sales
5. Weak Negative -- Rank, Sales
6. Weak Positive -- Price, Revenue
7. Weak Negative -- Rank, Revenue

Converting categorical data we want to use to numeric data
```{r}
genre_mappings <- c("fiction" = 1, "nonfiction" = 2, "children" = 3)
author_rating_mapping <- c("Novice" = 1, "Intermediate" = 2, "Excellent" = 3, "Famous" = 4)

genre_encoded <- genre_mappings[categorical_df$genre]
author_rating_encoded <- author_rating_mapping[categorical_df$Author_Rating]

print(genre_encoded)
print(author_rating_encoded)
```

Adding the converted categorical data back to the numeric data set
```{r}
numeric_df$genre <- genre_encoded
numeric_df$author_rating <- author_rating_encoded

print(numeric_df)
```

Running another correlation matrix with the newly added columns
```{r}
corr_matrix <- cor(numeric_df)
print(corr_matrix)
```
New Notable Relationships
Strong Positive -- Book Rating, Author Rating
Figuring out which numbers correspond to which categorical descriptors
```{r}
categorical_

find_values <- function(column, df){
  unique_vals <- unique(column)
  for (value in unique_vals) {
      category <- levels(factor(column))[value]
      print(paste("Numeric: ", value, " Category: ", category))
    }  
  }


find_values(author_rating_encoded)
```